Global liveability ranking

### 2022-07-20 inst/global_liveability_ranking.Rmd
more work

```{r showglrtable}
readLines("global_liveability_ranking.txt")
```

@@

```{r readglrtable}
o <- readLines("global_liveability_ranking.txt") %>% strsplit(" ") %>% lapply(function(l){l[-1]})
H <- hyper2()
for(i in seq_along(o)){
  H <- H  + race(o[[i]])
}
```

@@

```{r testgrl, cache=TRUE}
mH <- maxp(H)
pie(mH)
equalp.test(H)
```

@@

>>>>

```{r showglrtable}
(glr <- readLines("global_liveability_ranking.txt"))
```

@@

```{r readglrtable}
(o <- glr  %>% strsplit(" ") %>% lapply(function(l){l[-1]}))
```

Will remove Helsinki, Brisbane, and Hamburg on account of their having
very low rank scores (if we leave them in, the Hessian becomes
non-positive-definite at the evaluate).

```{r,removeHelsinki_and_Hamburg}
o %<>%  lapply(function(x){x[!(x %in% c("Hamburg","Helsinki","Brisbane"))]})
o
```

```{r,turnintohyper2,cache=TRUE}
H <- hyper2()
for(i in seq_along(o)){
  H <- H  + race(o[[i]])
}
```

@@

```{r testgrl, cache=TRUE}
(mH <- maxp(H))
pie(mH)
equalp.test(H)
```

```{r,calculatemoreinfo,cache=TRUE}
jjm <- maxp(H,n=1,give=TRUE,hessian=TRUE)
```

```{r}
jjm$hessian
diag(jjm$hessian)
eigen(jjm$hessian)$values
```

So the Hessian is positive-definite [all the eigenvalues are
positive].  Also, the evaluate is robust, as indicated by
`consistency()`:

```{r,doconsis,cache=TRUE}
consistency(H)
```

@@

# A More coarse division

We will try dividing the countries into continents:

```{r,label=elasticcontinent}
elastic_continent <- list(
Europe      = c("Vienna","Copenhagen","Zurich","Geneva","Frankfurt","Hamburg","Amsterdam","Helsinki"),
America     = c("Calgary","Vancouver","Toronto"),
Asia        = c("Osaka","Tokyo"),
Australasia = c("Melbourne","Adelaide","Perth","Brisbane","Sydney","Auckland","Wellington")
)

ec <- NULL
for(i in seq_along(elastic_continent)){
  jj <- rep(i,length(elastic_continent[[i]]))
  names(jj) <- elastic_continent[[i]]
  ec <- c(ec,jj)
}
ec 
MLc <- function(h){
   H3 <- hyper3()
   for(r in o){ H3 <- H3 + cheering3(r,e=ec,help=rep(h,4))}
   return(H3)
}
fc <- function(h){maxp(ML(h),give=TRUE,n=1)$likes}
```

```{r,evaluatefc,cache=TRUE}
l <- seq(from=0.8,to=3,len=10)
L <- sapply(l,fc)
```

```{r,plotfc}
plot(l,L-max(L),type="b")
```
